%!TEX root = tesi.tex
\cleardoublepage
\chapter{Introduction}
%\pagestyle{intro}
%The most recent developments in quantum field theory have been associated to 
After the triumph of the Standard Model in the seventies, many theoretical physicist shifted their attention towards the understanding of the dynamics of strongly coupled quantum field theories. \\
In that period, in fact, quantum field theories were properly understood only by using perturbation theory, which is only applicable if the theory is weakly coupled such as QED or QCD at high energies.
However, QCD is strongly coupled at energies lower than a few GeVs, thus making perturbative methods unavailable in this regime.
\\
In this context, dualities between theories at strong and weak coupling gained a lot of attention because they can be used to compute physical quantities of strongly coupled theories in the weakly-coupled theory through well-understood perturbative methods.
\\

Even though the Standard Model has predicted many phenomenas with great accuracy, it is believed that it is not able to describe the physical world for all the energies below the Planck scale.
If one would assume that a converse is true, some parameters such as the Higgs mass would require a fine tuning of the initial value that
seems oddly unnatural .
Such fine tuning is required since the Higgs mass receives quadratic corrections.
This is called usually referred as the \emph{hierarchy problem}.
\\
One of the possible solutions to this problem is supersymmetry, which is a symmetry between bosons and fermions. 
For each particle, there exists a supersymmetric partner with different spin  such that every boson has a fermionic partner and viceversa.
The presence of particles with different spin but identical quantum numbers removes all the quadratic corrections because loop contributions from bosons and fermions cancel each other out and only logarithmic corrections remain.
\\
Moreover, supersymmetry theories posses many other useful renormalization properties such that they are easier to analyse with respect to non-supersymmetric theories.\\


%Moreover, Coleman-Mandula theorem prohibits internal symmetries associated to a Lie algebra to transform non-trivially under the Lorentz group.
%However, this theorem cannot be applied to supersymmetry since supersymmetry is written as a grade one Lie algebra. 
%The simplest supersymmetric extension of the standard model associates a
%a supersymmetric partner to each particle present in the original standard model. The partner is 



The first example of strong-weak duality is the electric-magnetic duality of Maxwell's equations discovered by Dirac in 1931, which consists in the invariance of the equations of motion under the exchange of the electric and magnetic field. 
In the presence of charges, electric and magnetic charges are exchanged too. \\
For a quantum system to be invariant under such duality, electric and magnetic charges need to be inversely proportional to each other. 
Dirac's quantization condition for particles that posses either electric or magnetic charge reads $e g =  2 n \pi \hbar$, where $e$ is the electric charge and $g$ the magnetic charge.
\\

A generalization of Dirac's electric-magnetic duality is the Montonen-Olive duality.
It states that a supersymmetric  $\mN=4$ quantum field theory in four dimensions with gauge group $G$ is equivalent to another theory with gauge group $\tilde{G}$ and with complexified gauge coupling $\tau' = - \frac{1}{\tau}$ and with electric and magnetic degrees of freedom exchanged.
The dual gauge group $G'$ in some cases is different from the gauge group $G$ of the original theory.
\\

Another important strong-weak duality is the AdS/CFT correspondence. 
It is a duality  between a gravitational theory in an Anti-deSitter space (AdS) and a conformal gauge theory (CFT) which lives on the boundary of the AdS space. \\
It was first conjectured by Maldacena \cite{Maldacena:1997re} between $II_B$ string theory on $AdS_5 \times S^5$ and a $\mN=4$ Super Yang-Mills theory in four dimensions. 
It is a realization of the holographic principle, which states that gravitational theories have the same number of degrees of freedom as gauge theories in a lower number of dimensions.\\
As we anticipated, the correspondence can be used to map observables in the strongly coupled field theory to observables in the weakly coupled gravitational theory in Anti-deSitter.
%Many quantities that were computable on both sides were calculated as a check of the duality, but the correspondence has been used in many situations to improve our understanding of strongly coupled field theories and, at the same time, of gravitational theories \\
It is now one of the more active areas of research and it was generalized to Anti-deSitter spaces in different dimensions and to non-conformal field theories by considering spacetime configurations that are only asymptotically Anti-deSitter.
As a result, the AdS/CFT correspondence is more generally called gauge/gravity duality.  \\
Practical applications of the correspondence ranged from the calculation of the viscosity of the quark-gluon plasma to phenomenological models of high temperature superconductors in condensed matter physics.
Even if these line of research are relatively new, gauge/gravity duality can provide some insights on the behavior of strongly coupled systems in different branches of physics.   
\\ 
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% SEIBERG DUALITY
%\pagestyle%{intro}
%The electric-magnetic duality can be generalized in four dimensions in field theories with the minimal amount of supersymmetry.
%These dualities relate the infrared behaviour of two different field theories: the electric and the magnetic theory.



Seiberg duality is a generalization of the electric-magnetic duality to four dimensional supersymmetric field theories with the minimal amount of supersymmetry.
It relates the infrared behavior of two different supersymmetric theories, the electric and the magnetic theory.\\
The electric theory of the first Seiberg duality discovered features a $\mN=1$ four dimensional gauge theory with $SU(N_c)$ gauge group and with $N_f$ superquarks in the fundamental and antifundamental representation.
The magnetic theory is a $SU(N_f-N_c)$ gauge theory with $N_f$ fundamental and antifundamental quarks and with $N_f^2$ singlets fields. 
They are called mesons because they have the same quantum numbers of the mesons that can be constructed in the electric theory by combining a quark with an antiquark. 
However, in the magnetic theory they are fundamental fields and they are not composite degrees of freedom as in the electric theory.\\
Both the electric and magnetic theories feature a strongly-interacting superconformal fixed point for a specific range of the number of flavours and colours. 
The duality maps a strongly coupled theory into a weakly coupled one as the other dualities discussed above. 
Therefore, we can use the magnetic degrees of freedom to analyse the properties of the electric theory in the strongly coupled regime.\\
Many generalizations of Seiberg duality exist and they can be constructed by starting with a theory with a different gauge group or by adding matter fields in other representations.
%Our work will be focused on Seiberg duality with an additional matter field in the adjoint representation. 
\\
Seiberg duality was initially discovered in four dimensional field theories but just a few years later, a three dimensional analogue of Seiberg duality with $U(N_c)$ gauge group was found by Aharony.\\

For fifteen years it was not clear how to link dualities in four and three dimensions even if they had many similarities. 
A naive dimensional reduction of a theory is obtained by compactfiying a direction to a circle and then ignoring the Kaluza-Klein modes associated to the compactified dimension.
This kind of dimensional reduction does not preserve the duality between the electric and the magnetic theory.  \\
However, the duality can be preserved in the reduction if we consider the consider the effects of the finite size of the circle.
In particular, there is one Kaluza-Klein instantonic state that needs to be considered in order to preserve the duality.
In fact, the instanton generates a non-perturbative superpotential term that breaks the additional symmetries present in three dimensions.\\
Flowing to low-energies, the Kaluza-Klein modes on the circle decouple and the theory exhibits an effectively three-dimensional behaviour.
However, the instantonic superpotential is still present. 
It can be removed by performing a real mass flow by assigning to some quarks large real masses, obtaining a three dimensional duality withouth additional superpotential terms.

We can apply this reasoning to different four dimensional dualities. 
In some cases we find already known dualities, while in other situations we discover unkown three dimensional dualities. 
Given that most of the three dimensional dualities have been derived from four dimensional dualities, it is conjectured that this is true for every three dimensional duality.\\

The process of dimensional reduction is understood in field theory in most cases, but some difficulties could arise of the strong coupling regime.\\
However, the results obtained in this way can be checked with an independent method which consists in the reduction of the duality directly through the partition function.
%However, there is an independent way to check the results obtained with these methods.\\
%t is the partition function approach we will use in our work.
The reduction process starts by calculating the superconformal index in four dimensions, for both dual theories. 
The index is a quantity defined for supersymmetric field theories in four dimensions with one of the directions compactified into a circle.
It counts the multiplets that have a specific relation between energy and angular momentum (BPS short multiplets). 
After the dimensional reduction, once the Kaluza-Klein modes are integrated out these multiplets correspond to bosonic and fermionic modes on the three-sphere.  
As a result, the partition function on the three sphere can be obtained by considering the superconformal index in the limit of zero radius.\\
Mathematical identities guarantees that the indices of dual theories match.\\

We start the reduction by calculating the superconformal index for both dual theories and then we reduce the index to the partition function by shrinking the radius of the circle to zero.
By performing a flow with large real masses assigned to some of the quarks, the instantonic superpotential disappears and we obtain a duality between three dimensional theories with the all the symmetries that were broken by the instantonic superpotential.
This process can be done directly on the partition function and the result of the flow can be read easily from the partition function.\\

Our work focuses on the dimensional reduction of Seiberg duality with $SU(N_c)$ gauge group 
dand with an additional chiral field in the adjoint representation by using the partition function approach discussed earlier.
This duality is known in literature as the Kutasov-Schwimmer-Seiberg (KSS) duality.
Its three dimensional analogue is called Kim-Park duality and it has a similar matter content to the four dimensional duality with the addition of singlet fields in the magnetic theory that have the same charges of the monopole operators of the electric theory.
The electric theory of Kim-Park is either $U(N_c)$ or $SU(N_c)$ which correspond to different magnetic theories. 
 \\
The dimensional reduction of the KSS duality to the Kim-Park duality with $U(N_c)$ or $SU(N_c)$ gauge groups has been performed by Nii with field theory techniques.\\
The scope of our work is to provide an independent check of his work by performing the dimensional reduction of KSS duality to $SU(N_c)$ Kim-Park duality on the partition function.\\
The advantage of this approach is that it is easier to work on the partition function rather than in field theory mostly because of the non-perturbative regime.
Moreover, in field theory one has to make some assumptions that are not still completely justified, while in the partition function approach those assumptions are not needed.
Whereas the reduction on the partition function to $U(N_c)$ Kim-Park duality has already been done in literature, the reduction of the $SU(N_c)$ case wasn't performed yet.
Thus, our work provides an independ check of the results obtained with field theory techniques.\\
The identity between the electric and magnetic partition function is not yet demonstrated as a mathematical identity and it could be one of the situations where physics can unveil new non-trivial mathematical relations. 
\\

\pagestyle{intro}
We begin our discussion in section 2 with a brief review of some of the properties of supersymmetric quantum field theories and the features of $SU(N_c)$ SQCD that will be needed in order to understand Seiberg duality.
After these consideration we illustrate Seiberg and KSS duality.
\thispagestyle{intro}

In section 3 we consider the different properties of supersymmetric theories in three dimensions with respect to the four dimensional ones.
Then, we introduce Aharony duality for $U(N_c)$ gauge group and Kim-Park duality for $U(N_c)$ or $SU(N_c)$ gauge groups.

In the fourth section we review the process of dimensional reduction in field theory, applying it to Seiberg duality, which results in a three dimensional duality that wasn't known before the introduction of this method. 
We  consider also the flow to Aharony duality, obtained by gauging the baryonic symmetry.
Then, we consider the reduction of KSS duality to Kim-Park with $U(N_c)$ and with $SU(N_c)$ gauge group.

In section 5 we give a brief introduction of the superconformal index, highlighting the key features that we will need in our analysis and we will also review the method of localization, which allows to compute partition functions exactly.
Moreover, we give an overview of the dimensional reduction procedure on the index to the partition function.

The last section is dedicated to our work and contains the key steps of the dimensional reduction with the partition function approach. 
Explicit calculations can be found in the appendix.



